Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-22 MS_revised.tex
table 2

% Table 2
\begin{table}[!h]
    \caption{\bf{Differences in rates estimated by MEDUSA on the MCC
tree from the sample of trees from the posterior distribution and the
MultiMEDUSA approach. Shift consistently recovered across the
sample of trees in bold face.}}
\begin{tabular}{lcrr}
Shift.Node & rate by MEDUSA & Median rate by MultiMEDUSA & probability of being recovered \\
1          & 0.092          & not found                  & 0.000                          \\
2          & 0.055          & -0.030                     & 0.864                          \\
\bf{3}     & 0.184          & \bf{0.219}                 & \bf{0.961}                     \\
\bf{4}     & 0.166          & \bf{0.212}                 & \bf{0.996}                     \\
\bf{5}     & 0.111          & \bf{0.101}                 & \bf{0.927}                     \\
6          & 0.119          & 0.039                      & 0.131                          \\
7          & 0.066          & -0.052                     & 0.195                          \\
8          & 0.232          & 0.166                      & 0.319                          \\
9          & 0.042          & -0.049                     & 0.897                          \\
10         & 0.058          & 0.149                      & 0.619                          \\
11         & 0.311          & 0.208                      & 0.831                          \\
\bf{12}    & 0.219          & \bf{0.135}                 & \bf{0.911}                     \\
13         & 0.082          & 0.117                      & 0.276                          \\
14         & 0.099          & 0.115                      & 0.379                          \\
15         & 0.113          & 0.127                      & 0.825                          \\
16         & 0.222          & -0.005                     & 0.659                          \\
17         & 0.243          & 0.248                      & 0.785                          \\
18         & 0.192          & -0.064                     & 0.024                          \\
19         & 0.064          & -0.087                     & 0.381                         
\end{tabular}
\end{table}

>>>>

% Table 2
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{{\bf Differences in rates estimated by MEDUSA on the MCC
tree from the sample of trees from the posterior distribution and the
MultiMEDUSA approach. Shift consistently recovered across the
sample of trees in bold face.}}
\begin{tabular}{|l|c|r|r|}
    \hline
Shift.Node & rate by MEDUSA & Median rate by MultiMEDUSA & probability of being recovered \\ \hline
1          & 0.092          & not found                  & 0.000                          \\ \hline
2          & 0.055          & -0.030                     & 0.864                          \\ \hline
\bf{3}     & 0.184          & \bf{0.219}                 & \bf{0.961}                     \\ \hline
\bf{4}     & 0.166          & \bf{0.212}                 & \bf{0.996}                     \\ \hline
\bf{5}     & 0.111          & \bf{0.101}                 & \bf{0.927}                     \\ \hline
6          & 0.119          & 0.039                      & 0.131                          \\ \hline
7          & 0.066          & -0.052                     & 0.195                          \\ \hline
8          & 0.232          & 0.166                      & 0.319                          \\ \hline
9          & 0.042          & -0.049                     & 0.897                          \\ \hline
10         & 0.058          & 0.149                      & 0.619                          \\ \hline
11         & 0.311          & 0.208                      & 0.831                          \\ \hline
\bf{12}    & 0.219          & \bf{0.135}                 & \bf{0.911}                     \\ \hline
13         & 0.082          & 0.117                      & 0.276                          \\ \hline
14         & 0.099          & 0.115                      & 0.379                          \\ \hline
15         & 0.113          & 0.127                      & 0.825                          \\ \hline
16         & 0.222          & -0.005                     & 0.659                          \\ \hline
17         & 0.243          & 0.248                      & 0.785                          \\ \hline
18         & 0.192          & -0.064                     & 0.024                          \\ \hline
19         & 0.064          & -0.087                     & 0.381                          \\ \hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\label{table2}
\end{adjustwidth}
\end{table}
